INGOs and instrumental factors

### 2023-05-12 notebook/desc-instrumental.qmd
Rename target for consistency

tar_load(c(survey_orgs, survey_countries, survey_all))
tar_load(c(strategies_size_models))

@@

```{r plot-strategies-size}
p1 <- strategies_size_models$draws %>% 
  ggplot(aes(x = .epred, y = fct_rev(small_org), fill = small_org)) +
  stat_halfeye() +
  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[5]),
                    guide = "none") +
  labs(x = "Average number of strategies", y = NULL) +
  theme_ingo()

p2 <- strategies_size_models$diffs %>% 
  ggplot(aes(x = .epred)) +
  stat_halfeye(fill = clrs$Prism[11]) +
  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  labs(x = "Average # of strategies for 51+ employees − average for 0–50 employees",
       y = NULL) +
  theme_ingo() +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank())

@@

```{r tab-strategies-size}
strategies_size_models$draws %>% 
  median_qi(.epred) %>% 
  mutate(small_org = as.character(small_org),
         type = "Group medians") %>%
  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
  bind_rows(strategies_size_models$diffs_summary) %>% 
  mutate(across(c(y, ymin, ymax, p_greater_0), 
                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
  mutate(nice_value = glue("{y_nice}<br>({ymin_nice}–{ymax_nice})")) %>% 
  mutate(small_org = str_replace(small_org, " - ", " − ")) %>% 
  select(type, small_org, nice_value, p_greater_0_nice) %>% 
  group_by(type) %>% 
  gt() %>% 
  cols_label(
    small_org = "",
    nice_value = "Posterior median",
    p_greater_0_nice = "p > 0"
  ) %>% 
  fmt_markdown(nice_value) %>% 
  sub_missing(p_greater_0_nice) %>% 
  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
  opts_theme()
```

>>>>

tar_load(c(survey_orgs, survey_countries, survey_all))
tar_load(c(models_strategies_size))

@@

```{r plot-strategies-size}
p1 <- models_strategies_size$draws %>% 
  ggplot(aes(x = .epred, y = fct_rev(small_org), fill = small_org)) +
  stat_halfeye() +
  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[5]),
                    guide = "none") +
  labs(x = "Average number of strategies", y = NULL) +
  theme_ingo()

p2 <- models_strategies_size$diffs %>% 
  ggplot(aes(x = .epred)) +
  stat_halfeye(fill = clrs$Prism[11]) +
  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  labs(x = "Average # of strategies for 51+ employees − average for 0–50 employees",
       y = NULL) +
  theme_ingo() +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank())

@@

```{r tab-strategies-size}
models_strategies_size$draws %>% 
  median_qi(.epred) %>% 
  mutate(small_org = as.character(small_org),
         type = "Group medians") %>%
  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
  bind_rows(models_strategies_size$diffs_summary) %>% 
  mutate(across(c(y, ymin, ymax, p_greater_0), 
                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
  mutate(nice_value = glue("{y_nice}<br>({ymin_nice}–{ymax_nice})")) %>% 
  mutate(small_org = str_replace(small_org, " - ", " − ")) %>% 
  select(type, small_org, nice_value, p_greater_0_nice) %>% 
  group_by(type) %>% 
  gt() %>% 
  cols_label(
    small_org = "",
    nice_value = "Posterior median",
    p_greater_0_nice = "p > 0"
  ) %>% 
  fmt_markdown(nice_value) %>% 
  sub_missing(p_greater_0_nice) %>% 
  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
  opts_theme()
```
